---
title: "TSS-Histones"
author: "Me"
date: "17 2 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

## Data Preparing 
## Exons

```{r }
data_exons <- read.table("EX_unreg_hist_try1.tab",header= TRUE,fill = TRUE)
data_exons <- data_exons[order(data_exons$GENE),]
data_TSS <- read.table('all_tss',header= TRUE,fill = TRUE)
data_TSS <- data_TSS[order(data_TSS$name2),]
data_TSS <- data_TSS[which(data_TSS$name2 %in% data_exons$GENE),]

# write.table(data_exons, file = "EX_unreg_hist_codinggenes.tab", quote = FALSE, sep = "\t",
#              row.names = FALSE)
# write.table(data_TSS, file = "TSS_exons_unreg_codinggens.tab", quote = FALSE, sep = "\t",
#              row.names = FALSE)
```

## Data Preparing 
## Introns


```{r}
data_introns <- read.table("INT_unreg.tab",header= TRUE,fill = TRUE)
data_introns <- data_introns[order(data_introns$GENE),]
data_TSS <- read.table('all_tss',header= TRUE,fill = TRUE)
data_TSS <- data_TSS[order(data_TSS$name2),]
data_TSS <- data_TSS[which(data_TSS$name2 %in% data_introns$GENE),]

write.table(data_introns, file = "INT_unreg_hist.tab", quote = FALSE, sep = "\t",
             row.names = FALSE)
write.table(data_TSS, file = "TSS_introns_unreg.tab", quote = FALSE, sep = "\t",
             row.names = FALSE)
```



## Data Spliting

```{r}
data_to_split_strand <- read.table('introns_tss_unreg.bed',header = TRUE)
x <- split(data_to_split_strand,data_to_split_strand$strand)
minus_strand <- x[[1]]
plus_strand <- x[[2]]
write.table(minus_strand, file = "introns_minus_strand_tss_unreg.tab", quote = FALSE, sep = "\t",
            row.names = FALSE, col.names = FALSE)
write.table(plus_strand, file = "introns_plus_strand_tss_unreg.tab", quote = FALSE, sep = "\t",
            row.names = FALSE, col.names = FALSE)
```



## Plots - H1.2 - Endo(WT) unaffected vs affected

```{r}
library(dplyr)
library(ggplot2)
H12_data <- read.table("H12_endo_plot_exons_new_level.tab",header= TRUE,fill = TRUE)
len <- nrow(H12_data)
pos <- seq(from = 1, to = len, by = 1)
H12_data <- cbind(H12_data,pos)
total_days <- diff(range(H12_data$pos))
span <- 100/total_days

fit_unaffected <- loess(H12_data$Unaffected ~ pos, degree=1, span = span, data=H12_data)
fit_affected <- loess(H12_data$Affected ~ pos, degree=1, span = span, data=H12_data)
colors <- c("Unaffected" = "deepskyblue", "Affected" = "navyblue")
H12_data %>% mutate(smooth_unaffected = fit_unaffected$fitted, smooth_affected = fit_affected$fitted) %>% ggplot(aes(pos, H12_data$Unaffected)) + geom_line(aes(y = smooth_unaffected,color = "Unaffected"), size = 1.5) + geom_line(aes(y = smooth_affected,color = "Affected"), size = 1.5) + geom_vline(xintercept = 2000, linetype = "longdash") + labs(x = "bps",
         y = "H1.2 Coverage",
         color = "") +
    scale_color_manual(values = colors) + theme_bw() + scale_x_continuous(breaks = waiver(), labels = c(-2000,-1500,-1000,-500,0,500))
```


## Plots - H1.5 - Endo(WT) unaffected vs affected

```{r}
library(dplyr)
library(ggplot2)
H15_data <- read.table("H15_endo_plot_exons_new_level.tab",header= TRUE,fill = TRUE)
len <- nrow(H15_data)
pos <- seq(from = 1, to = len, by = 1)
H15_data <- cbind(H15_data,pos)
total_days <- diff(range(H15_data$pos))
span <- 100/total_days

fit_unaffected <- loess(H15_data$Unaffected ~ pos, degree=1, span = span, data=H15_data)
fit_affected <- loess(H15_data$Affected ~ pos, degree=1, span = span, data=H15_data)
colors <- c("Unaffected" = "red1", "Affected" = "red4")
H15_data %>% mutate(smooth_unaffected = fit_unaffected$fitted, smooth_affected = fit_affected$fitted) %>% ggplot(aes(pos, H15_data$Unaffected)) + geom_line(aes(y = smooth_unaffected,color = "Unaffected"), size = 1.5) + geom_line(aes(y = smooth_affected,color = "Affected"), size = 1.5) + geom_vline(xintercept = 2000, linetype = "longdash") + labs(x = "bps",
         y = "H1.5 Coverage",
         color = "") +
    scale_color_manual(values = colors) + theme_bw() + scale_x_continuous(breaks = waiver(), labels = c(-2000,-1500,-1000,-500,0,500))
```


## Checking smooth
## H1.2

```{r}
smooth_unaff <- smooth.spline(H12_data$Unaffected,nknots = 15)
smooth_aff <- smooth.spline(H12_data$Affected,nknots = 15)
data_after_smooth <- data.frame(smooth_aff$y,smooth_unaff$y)
colnames(data_after_smooth) <- c('Affected','Unaffected')
data_after_smooth <- data_after_smooth[-c(1:1000),]
len <- nrow(data_after_smooth)
pos <- seq(from = 1, to = len, by = 1)
data_after_smooth <- cbind(data_after_smooth,pos)
total_days <- diff(range(data_after_smooth$pos))
span <- 100/total_days

fit_unaffected <- loess(data_after_smooth$Unaffected ~ pos, degree=1, span = span, data=data_after_smooth)
fit_affected <- loess(data_after_smooth$Affected ~ pos, degree=1, span = span, data=data_after_smooth)
colors <- c("Unaffected" = "deepskyblue", "Affected" = "navyblue")
data_after_smooth %>% mutate(smooth_unaffected = fit_unaffected$fitted, smooth_affected = fit_affected$fitted) %>% ggplot(aes(pos, data_after_smooth$Unaffected)) + geom_line(aes(y = smooth_unaffected,color = "Unaffected"), size = 1.5) + geom_line(aes(y = smooth_affected,color = "Affected"), size = 1.5) + geom_vline(xintercept = 1000, linetype = "longdash") + labs(x = "bps",
         y = "H1.2 Coverage",
         color = "") +
    scale_color_manual(values = colors) + theme_bw() + scale_x_continuous(breaks = waiver(), labels = c(-1000,-500,"TSS",500))
```

##H1.5


```{r}
smooth_unaff <- smooth.spline(H15_data$Unaffected,nknots = 11)
smooth_aff <- smooth.spline(H15_data$Affected,nknots = 11)
data_after_smooth <- data.frame(smooth_aff$y,smooth_unaff$y)
colnames(data_after_smooth) <- c('Affected','Unaffected')
data_after_smooth <- data_after_smooth[-c(1:1000),]
len <- nrow(data_after_smooth)
pos <- seq(from = 1, to = len, by = 1)
data_after_smooth <- cbind(data_after_smooth,pos)
total_days <- diff(range(data_after_smooth$pos))
span <- 100/total_days

fit_unaffected <- loess(data_after_smooth$Unaffected ~ pos, degree=1, span = span, data=data_after_smooth)
fit_affected <- loess(data_after_smooth$Affected ~ pos, degree=1, span = span, data=data_after_smooth)
colors <- c("Unaffected" = "deepskyblue", "Affected" = "navyblue")
data_after_smooth %>% mutate(smooth_unaffected = fit_unaffected$fitted, smooth_affected = fit_affected$fitted) %>% ggplot(aes(pos, data_after_smooth$Unaffected)) + geom_line(aes(y = smooth_unaffected,color = "Unaffected"), size = 1.5) + geom_line(aes(y = smooth_affected,color = "Affected"), size = 1.5) + geom_vline(xintercept = 1000, linetype = "longdash") + labs(x = "bps",
         y = "H1.5 Coverage",
         color = "") +
    scale_color_manual(values = colors) + theme_bw() + scale_x_continuous(breaks = waiver(), labels = c(-1000,-500,"TSS",500))
```



## mean plot- H1.2


```{r}
library(ggpubr)
library(plotrix)
pdf("mean_plot_h12_ill.pdf")
affected <- data.frame(H12_data[,1])
unaffected <- data.frame(H12_data[,2])
affected$Group <- as.factor('affected')
names(affected)[1] <- 'H1.2-Coverage'
unaffected$Group <- as.factor('unaffected')
names(unaffected)[1] <- 'H1.2-Coverage'
data_to_plot_affect <- rbind(affected,unaffected)
compare_means(`H1.2-Coverage` ~ Group, data =  data_to_plot_affect, method = "t.test")
p <- ggboxplot(data_to_plot_affect, x = "Group", y = "H1.2-Coverage",
          color = rev(c("Unaffected" = "deepskyblue", "Affected" = "navyblue"))) +
  stat_compare_means(label = "p.signif",ref.group = "unaffected")
p + rremove("x.text") + rremove("x.title")
print(p)
dev.off()
 data_summary <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = std.error(x[[col]]))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- plyr::rename(data_sum, c("mean" = varname))
 return(data_sum)
}

data_to_plot_affect <- data_summary(data_to_plot_affect, varname="H1.2-Coverage", 
                    groupnames=c("Group"))
x_categories = rev(c("deepskyblue", "navyblue"))
ggplot(data_to_plot_affect, aes(x=Group, y=`H1.2-Coverage`)) + geom_pointrange(aes(ymin=`H1.2-Coverage`-sd, ymax=`H1.2-Coverage`+sd), size = 2, fatten = 1.5, show.legend = FALSE, color = x_categories) + scale_colour_manual(values = c("affected" = "red4", "unaffected" = "red1")) + theme_bw() + annotate("text", x = "unaffected", y = 0.165, label = "****") + scale_x_discrete(breaks = NULL) +
  theme(
    axis.title.y = element_text(size = 15) 
  ) + labs(x = "",
         y = "H1.2 Coverage",
         color = "")
 
```


## mean plot- H1.5

```{r}
library(ggpubr)
library(plotrix)
pdf("mean_plot_h15_ill.pdf")
affected <- data.frame(H15_data[,1])
unaffected <- data.frame(H15_data[,2])
affected$Group <- as.factor('affected')
names(affected)[1] <- 'H1.5-Coverage'
unaffected$Group <- as.factor('unaffected')
names(unaffected)[1] <- 'H1.5-Coverage'
data_to_plot_affect <- rbind(affected,unaffected)
compare_means(`H1.5-Coverage` ~ Group, data =  data_to_plot_affect)
p <- ggboxplot(data_to_plot_affect, x = "Group", y = "H1.5-Coverage",
          color = rev(c("Unaffected" = "deepskyblue", "Affected" = "navyblue"))) +
  stat_compare_means(label = "p.signif",ref.group = "unaffected")
p + rremove("x.text") + rremove("x.title")
print(p)
dev.off()
 data_summary <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = std.error(x[[col]]))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- plyr::rename(data_sum, c("mean" = varname))
 return(data_sum)
}

data_to_plot_affect <- data_summary(data_to_plot_affect, varname="H1.5-Coverage", 
                    groupnames=c("Group"))
x_categories = rev(c("deepskyblue", "navyblue"))
ggplot(data_to_plot_affect, aes(x=Group, y=`H1.5-Coverage`)) + geom_pointrange(aes(ymin=`H1.5-Coverage`-sd, ymax=`H1.5-Coverage`+sd), size = 2, fatten = 1.5, show.legend = FALSE, color = x_categories) + scale_colour_manual(values = c("affected" = "red4", "unaffected" = "red1")) + theme_bw() + annotate("text", x = "unaffected", y = 0.14, label = "****") + scale_x_discrete(breaks = NULL) +
  theme(
    axis.title.y = element_text(size = 15) 
  ) + labs(x = "",
         y = "H1.5 Coverage",
         color = "")
```



## Plots_introns - H1.2 - Endo(WT) unaffected vs affected

```{r}
library(dplyr)
library(ggplot2)
H12_data <- read.table("H12_endo_plot_introns_new_level.tab",header= TRUE,fill = TRUE)


smooth_unaff <- smooth.spline(H12_data$Unaffected,nknots = 14)
smooth_aff <- smooth.spline(H12_data$Affected,nknots = 14)
data_after_smooth <- data.frame(smooth_aff$y,smooth_unaff$y)
colnames(data_after_smooth) <- c('Affected','Unaffected')
data_after_smooth <- data_after_smooth[-c(1:1000),]
len <- nrow(data_after_smooth)
pos <- seq(from = 1, to = len, by = 1)
data_after_smooth <- cbind(data_after_smooth,pos)
total_days <- diff(range(data_after_smooth$pos))
span <- 100/total_days

fit_unaffected <- loess(data_after_smooth$Unaffected ~ pos, degree=1, span = span, data=data_after_smooth)
fit_affected <- loess(data_after_smooth$Affected ~ pos, degree=1, span = span, data=data_after_smooth)
colors <- c("Unaffected" = "red1", "Affected" = "red4")
data_after_smooth %>% mutate(smooth_unaffected = fit_unaffected$fitted, smooth_affected = fit_affected$fitted) %>% ggplot(aes(pos, data_after_smooth$Unaffected)) + geom_line(aes(y = smooth_unaffected,color = "Unaffected"), size = 1.5) + geom_line(aes(y = smooth_affected,color = "Affected"), size = 1.5) + geom_vline(xintercept = 1000, linetype = "longdash") + labs(x = "bps",
         y = "H1.2 Coverage",
         color = "") +
    scale_color_manual(values = colors) + theme_bw() + scale_x_continuous(breaks = waiver(), labels = c(-1000,-500,"TSS",500))

pdf("mean_plot_h12_intron.pdf")
affected <- data.frame(H12_data[,1])
unaffected <- data.frame(H12_data[,2])
affected$Group <- as.factor('affected')
names(affected)[1] <- 'H1.2-Coverage'
unaffected$Group <- as.factor('unaffected')
names(unaffected)[1] <- 'H1.2-Coverage'
data_to_plot_affect <- rbind(affected,unaffected)
compare_means(`H1.2-Coverage` ~ Group, data =  data_to_plot_affect)
p <- ggboxplot(data_to_plot_affect, x = "Group", y = "H1.2-Coverage",
          color = rev(c("Unaffected" = "red1", "Affected" = "red4"))) +
  stat_compare_means(label = "p.signif",ref.group = "unaffected")
p + rremove("x.text") + rremove("x.title")
print(p)
dev.off()
 data_summary <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = std.error(x[[col]]))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- plyr::rename(data_sum, c("mean" = varname))
 return(data_sum)
}

data_to_plot_affect <- data_summary(data_to_plot_affect, varname="H1.2-Coverage", 
                    groupnames=c("Group"))
x_categories = c("red4", "red1");
ggplot(data_to_plot_affect, aes(x=Group, y=`H1.2-Coverage`)) + geom_pointrange(aes(ymin=`H1.2-Coverage`-sd, ymax=`H1.2-Coverage`+sd), size = 2, fatten = 1.5, show.legend = FALSE, color = x_categories) + scale_colour_manual(values = c("affected" = "red4", "unaffected" = "red1")) + theme_bw() + annotate("text", x = "unaffected", y = 0.15, label = "****") + scale_x_discrete(breaks = NULL) +
  theme(
    axis.title.y = element_text(size = 15) 
  ) + labs(x = "",
         y = "H1.2 Coverage",
         color = "")
```



## Plots_introns - H1.5 - Endo(WT) unaffected vs affected

```{r}
H15_data <- read.table("H15_endo_plot_introns_new_level.tab",header= TRUE,fill = TRUE)
smooth_unaff <- smooth.spline(H15_data$Unaffected,nknots = 10)
smooth_aff <- smooth.spline(H15_data$Affected,nknots = 10)
data_after_smooth <- data.frame(smooth_aff$y,smooth_unaff$y)
colnames(data_after_smooth) <- c('Affected','Unaffected')
data_after_smooth <- data_after_smooth[-c(1:1000),]
len <- nrow(data_after_smooth)
pos <- seq(from = 1, to = len, by = 1)
data_after_smooth <- cbind(data_after_smooth,pos)
total_days <- diff(range(data_after_smooth$pos))
span <- 100/total_days

fit_unaffected <- loess(data_after_smooth$Unaffected ~ pos, degree=1, span = span, data=data_after_smooth)
fit_affected <- loess(data_after_smooth$Affected ~ pos, degree=1, span = span, data=data_after_smooth)
colors <- c("Unaffected" = "red1", "Affected" = "red4")
data_after_smooth %>% mutate(smooth_unaffected = fit_unaffected$fitted, smooth_affected = fit_affected$fitted) %>% ggplot(aes(pos, data_after_smooth$Unaffected)) + geom_line(aes(y = smooth_unaffected,color = "Unaffected"), size = 1.5) + geom_line(aes(y = smooth_affected,color = "Affected"), size = 1.5) + geom_vline(xintercept = 1000, linetype = "longdash") + labs(x = "bps",
         y = "H1.5 Coverage",
         color = "") +
    scale_color_manual(values = colors) + theme_bw() + scale_x_continuous(breaks = waiver(), labels = c(-1000,-500,"TSS",500))

pdf("mean_plot_h15_intron.pdf")
affected <- data.frame(H15_data[,1])
unaffected <- data.frame(H15_data[,2])
affected$Group <- as.factor('affected')
names(affected)[1] <- 'H1.5-Coverage'
unaffected$Group <- as.factor('unaffected')
names(unaffected)[1] <- 'H1.5-Coverage'
data_to_plot_affect <- rbind(affected,unaffected)
compare_means(`H1.5-Coverage` ~ Group, data =  data_to_plot_affect)
 p <- ggboxplot(data_to_plot_affect, x = "Group", y = "H1.5-Coverage",
          color = rev(c("Unaffected" = "red1", "Affected" = "red4"))) +
  stat_compare_means(label = "p.signif",ref.group = "unaffected")
 p + rremove("x.text") + rremove("x.title")
print(p)
dev.off()

 data_summary <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = std.error(x[[col]]))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- plyr::rename(data_sum, c("mean" = varname))
 return(data_sum)
}

data_to_plot_affect <- data_summary(data_to_plot_affect, varname="H1.5-Coverage", 
                    groupnames=c("Group"))
x_categories = c("red4", "red1");
ggplot(data_to_plot_affect, aes(x=Group, y=`H1.5-Coverage`)) + geom_pointrange(aes(ymin=`H1.5-Coverage`-sd, ymax=`H1.5-Coverage`+sd), size = 2, fatten = 1.5, show.legend = FALSE, color = x_categories) + scale_colour_manual(values = c("affected" = "red4", "unaffected" = "red1")) + theme_bw() + annotate("text", x = "unaffected", y = 0.13, label = "****") + scale_x_discrete(breaks = NULL) +
  theme(
    axis.title.y = element_text(size = 15) 
  ) + labs(x = "",
         y = "H1.5 Coverage",
         color = "")

```



## Check Transcription level of both groups on logCPM

```{r}
library(ggpubr)
library(plotrix)
data_exons_unreg <- read.table("INT_unreg_hist.tab",header= TRUE,fill = TRUE)
data_exons_unreg <- data_exons_unreg[order(data_exons_unreg$GENE),]
transcrpit_data <- read.table("all_genes.tab",header= TRUE,fill = TRUE)
transcrpit_data <- transcrpit_data[which(transcrpit_data$genes %in% unique(data_exons_unreg$GENE)),]
transcrpit_data <- transcrpit_data[order(transcrpit_data$genes),]
data_exons_diff <- read.table("INT_diffas_hist.tab",header= TRUE,fill = TRUE)
data_exons_diff <- data_exons_diff[order(data_exons_diff$GENE),]
transcrpit_data_diff <- read.table("all_genes.tab",header= TRUE,fill = TRUE)
transcrpit_data_diff <- transcrpit_data_diff[which(transcrpit_data_diff$genes %in% unique(data_exons_diff$GENE)),]
transcrpit_data_diff <- transcrpit_data_diff[order(transcrpit_data_diff$genes),]
affected <- data.frame(transcrpit_data_diff$logCPM)
unaffected <- data.frame(transcrpit_data$logCPM)
affected$Group <- as.factor('affected')
names(affected)[1] <- 'logCPM'
unaffected$Group <- as.factor('unaffected')
names(unaffected)[1] <- 'logCPM'
data_to_plot_affect <- rbind(affected,unaffected)
compare_means(`logCPM` ~ Group, data =  data_to_plot_affect)
data_summary <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = std.error(x[[col]]))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- plyr::rename(data_sum, c("mean" = varname))
 return(data_sum)
}

data_to_plot_affect <- data_summary(data_to_plot_affect, varname="logCPM", 
                    groupnames=c("Group"))
```



## Check Transcription level of both groups and make new on the same level 

```{r}
data_exons_unreg <- read.table("INT_unreg_hist.tab",header= TRUE,fill = TRUE)
data_exons_unreg <- data_exons_unreg[order(data_exons_unreg$GENE),]
data_exons_diff <- read.table("INT_diffas_hist.tab",header= TRUE,fill = TRUE)
data_exons_diff <- data_exons_diff[order(data_exons_diff$GENE),]
data_exons_unreg <- data_exons_unreg[which(data_exons_unreg$GENE %in% data_exons_diff$GENE),]
data_TSS <- read.table('all_tss',header= TRUE,fill = TRUE)
data_TSS <- data_TSS[order(data_TSS$name2),]
data_TSS_unreg <- data_TSS[which(data_TSS$name2 %in% data_exons_unreg$GENE),]
data_TSS_diff <- data_TSS[which(data_TSS$name2 %in% data_exons_diff$GENE),]

write.table(data_exons_unreg, file = "INT_unreg_hist_same_level.tab", quote = FALSE, sep = "\t",
              row.names = FALSE)
write.table(data_TSS_unreg, file = "TSS_introns_unreg_same_level.tab", quote = FALSE, sep = "\t",
              row.names = FALSE)

write.table(data_exons_diff, file = "INT_diff_hist_same_level.tab", quote = FALSE, sep = "\t",
              row.names = FALSE)
write.table(data_TSS_diff, file = "TSS_introns_diff_same_level.tab", quote = FALSE, sep = "\t",
              row.names = FALSE)

```







## Plots_exons - H1.2 - Endo(WT) unaffected vs affected


```{r}
library(dplyr)
library(ggplot2)
H12_exons_data <- read.table('file_exon_affected_h12_flip.txt',sep=",")
Unaffected <- as.numeric(H12_exons_data[1,])
Affected <- as.numeric(H12_exons_data[2,])
H12_exons_data <- data.frame(Unaffected,Affected)
H12_exons_data <- H12_exons_data[-c(110:115,116:153,153:160,298:335),]
smooth_unaff <- smooth.spline(H12_exons_data$Unaffected,nknots = 10)
smooth_aff <- smooth.spline(H12_exons_data$Affected,nknots = 10)
data_after_smooth <- data.frame(smooth_aff$y,smooth_unaff$y)
colnames(data_after_smooth) <- c('Affected','Unaffected')
len <- nrow(data_after_smooth)
pos <- seq(from = 1, to = len, by = 1)
data_after_smooth <- cbind(data_after_smooth,pos)
total_days <- diff(range(data_after_smooth$pos))
span <- 21/total_days

fit_unaffected <- loess(data_after_smooth$Unaffected ~ pos, degree=1, span = span, data=data_after_smooth)
fit_affected <- loess(data_after_smooth$Affected ~ pos, degree=1, span = span, data=data_after_smooth)
colors <- c("Unaffected" = "deepskyblue", "Affected" = "navyblue")
data_after_smooth %>% mutate(smooth_unaffected = fit_unaffected$fitted, smooth_affected = fit_affected$fitted) %>% ggplot(aes(pos, data_after_smooth$Unaffected)) + geom_line(aes(y = smooth_unaffected,color = "Unaffected"), size = 1.5) + geom_line(aes(y = smooth_affected,color = "Affected"), size = 1.5) + geom_vline(xintercept = 109, linetype = "longdash") + geom_vline(xintercept = 178, linetype = "longdash") + geom_vline(xintercept = 247, linetype = "longdash") + labs(x = "",
         y = "H1.2 Coverage",
         color = "") +
    scale_color_manual(values = colors) + theme_bw() +  scale_x_continuous(breaks = NULL)



affected <- data.frame(H12_exons_data[,2])
unaffected <- data.frame(H12_exons_data[,1])
affected$Group <- as.factor('affected')
names(affected)[1] <- 'Mean'
unaffected$Group <- as.factor('unaffected')
names(unaffected)[1] <- 'Mean'
data_to_plot_affect <- rbind(affected,unaffected)
compare_means(Mean ~ Group, data =  data_to_plot_affect)
p <- ggboxplot(data_to_plot_affect, x = "Group", y = "Mean",
          color = rev(c("Unaffected" = "deepskyblue", "Affected" = "navyblue")), ylab = "H1.2 Coverage") +
  stat_compare_means(label = "p.signif",ref.group = "affected")
p + rremove("x.text") + rremove("x.title")


```

## Plots_exons - H1.5 - Endo(WT) unaffected vs affected

```{r}
library(dplyr)
library(ggplot2)
H15_exons_data <- read.table('file_exon_affected_h15_flip.txt',sep=",")
Unaffected <- as.numeric(H15_exons_data[1,])
Affected <- as.numeric(H15_exons_data[2,])
H15_exons_data <- data.frame(Unaffected,Affected)
H15_exons_data <- H15_exons_data[-c(110:115,116:153,153:160,298:335),]
smooth_unaff <- smooth.spline(H15_exons_data$Unaffected,nknots = 10)
smooth_aff <- smooth.spline(H15_exons_data$Affected,nknots = 10)
data_after_smooth <- data.frame(smooth_aff$y,smooth_unaff$y)
colnames(data_after_smooth) <- c('Affected','Unaffected')
len <- nrow(data_after_smooth)
pos <- seq(from = 1, to = len, by = 1)
data_after_smooth <- cbind(data_after_smooth,pos)
total_days <- diff(range(data_after_smooth$pos))
span <- 21/total_days

fit_unaffected <- loess(data_after_smooth$Unaffected ~ pos, degree=1, span = span, data=data_after_smooth)
fit_affected <- loess(data_after_smooth$Affected ~ pos, degree=1, span = span, data=data_after_smooth)
colors <- c("Unaffected" = "deepskyblue", "Affected" = "navyblue")
data_after_smooth %>% mutate(smooth_unaffected = fit_unaffected$fitted, smooth_affected = fit_affected$fitted) %>% ggplot(aes(pos, data_after_smooth$Unaffected)) + geom_line(aes(y = smooth_unaffected,color = "Unaffected"), size = 1.5) + geom_line(aes(y = smooth_affected,color = "Affected"), size = 1.5) + geom_vline(xintercept = 109, linetype = "longdash") + geom_vline(xintercept = 178, linetype = "longdash") + geom_vline(xintercept = 247, linetype = "longdash") + labs(x = "",
         y = "H1.5 Coverage",
         color = "") +
    scale_color_manual(values = colors) + theme_bw() +  scale_x_continuous(breaks = NULL)


# pdf("mean_plot_h15_cov.pdf")
affected <- data.frame(H15_exons_data[,2])
unaffected <- data.frame(H15_exons_data[,1])
affected$Group <- as.factor('affected')
names(affected)[1] <- 'Mean'
unaffected$Group <- as.factor('unaffected')
names(unaffected)[1] <- 'Mean'
data_to_plot_affect <- rbind(affected,unaffected)
compare_means(Mean ~ Group, data =  data_to_plot_affect)
p <- ggboxplot(data_to_plot_affect, x = "Group", y = "Mean",
          color = rev(c("Unaffected" = "deepskyblue", "Affected" = "navyblue")), ylab = "H1.5 Coverage") +
  stat_compare_means(label = "p.signif",ref.group = "affected")
p + rremove("x.text") + rremove("x.title")
# print(p)
# dev.off()
```





## Plots_introns - H1.2 - Endo(WT) unaffected vs affected


```{r}
H12_introns_data <- read.table("file_with_introns_affect_h12_flip.txt",sep=",")
Unaffected <- as.numeric(H12_introns_data[1,])
Affected <- as.numeric(H12_introns_data[2,])
H12_introns_data <- data.frame(Unaffected,Affected)
H12_introns_data <- H12_introns_data[-c(1:2,73:82,331:377, 448:500),]
smooth_unaff <- smooth.spline(H12_introns_data$Unaffected,nknots = 4)
smooth_aff <- smooth.spline(H12_introns_data$Affected,nknots = 4)
data_after_smooth <- data.frame(smooth_aff$y,smooth_unaff$y)
colnames(data_after_smooth) <- c('Affected','Unaffected')
len <- nrow(data_after_smooth)
pos <- seq(from = 1, to = len, by = 1)
data_after_smooth <- cbind(data_after_smooth,pos)
total_days <- diff(range(data_after_smooth$pos))
span <- 21/total_days

fit_unaffected <- loess(data_after_smooth$Unaffected ~ pos, degree=1, span = span, data=data_after_smooth)
fit_affected <- loess(data_after_smooth$Affected ~ pos, degree=1, span = span, data=data_after_smooth)
colors <- c("Unaffected" = "red1", "Affected" = "red4")
data_after_smooth %>% mutate(smooth_unaffected = fit_unaffected$fitted, smooth_affected = fit_affected$fitted) %>% ggplot(aes(pos, data_after_smooth$Unaffected)) + geom_line(aes(y = smooth_unaffected,color = "Unaffected"), size = 1.5) + geom_line(aes(y = smooth_affected,color = "Affected"), size = 1.5) + geom_vline(xintercept = 70, linetype = "longdash") + geom_vline(xintercept = 200, linetype = "longdash") + geom_vline(xintercept = 330, linetype = "longdash") + labs(x = "",
         y = "H1.2 Coverage",
         color = "") +
    scale_color_manual(values = colors) + theme_bw() +  scale_x_continuous(breaks = NULL)
pdf("mean_plot_h12_intron_cov.pdf")
affected <- data.frame(H12_introns_data[,2])
unaffected <- data.frame(H12_introns_data[,1])
affected$Group <- as.factor('affected')
names(affected)[1] <- 'H1.2-Coverage'
unaffected$Group <- as.factor('unaffected')
names(unaffected)[1] <- 'H1.2-Coverage'
data_to_plot_affect <- rbind(affected,unaffected)
compare_means(`H1.2-Coverage` ~ Group, data =  data_to_plot_affect)
p <- ggboxplot(data_to_plot_affect, x = "Group", y = "H1.2-Coverage",
          color = rev(c("Unaffected" = "red1", "Affected" = "red4"))) +
  stat_compare_means(label = "p.signif",ref.group = "unaffected")
p + rremove("x.text") + rremove("x.title")

print(p)
dev.off()

```


## Plots_introns - H1.5 - Endo(WT) unaffected vs affected



```{r}
H15_introns_data <- read.table("file_with_introns_affect_h15_flip.txt",sep=",")
Unaffected <- as.numeric(H15_introns_data[1,])
Affected <- as.numeric(H15_introns_data[2,])
H15_introns_data <- data.frame(Unaffected,Affected)
H15_introns_data <- H15_introns_data[-c(1:2,73:82,331:377, 448:500),]
smooth_unaff <- smooth.spline(H15_introns_data$Unaffected,nknots = 4)
smooth_aff <- smooth.spline(H15_introns_data$Affected,nknots = 4)
data_after_smooth <- data.frame(smooth_aff$y,smooth_unaff$y)
colnames(data_after_smooth) <- c('Affected','Unaffected')
len <- nrow(data_after_smooth)
pos <- seq(from = 1, to = len, by = 1)
data_after_smooth <- cbind(data_after_smooth,pos)
total_days <- diff(range(data_after_smooth$pos))
span <- 21/total_days

fit_unaffected <- loess(data_after_smooth$Unaffected ~ pos, degree=1, span = span, data=data_after_smooth)
fit_affected <- loess(data_after_smooth$Affected ~ pos, degree=1, span = span, data=data_after_smooth)
colors <- c("Unaffected" = "red1", "Affected" = "red4")
data_after_smooth %>% mutate(smooth_unaffected = fit_unaffected$fitted, smooth_affected = fit_affected$fitted) %>% ggplot(aes(pos, data_after_smooth$Unaffected)) + geom_line(aes(y = smooth_unaffected,color = "Unaffected"), size = 1.5) + geom_line(aes(y = smooth_affected,color = "Affected"), size = 1.5) + geom_vline(xintercept = 70, linetype = "longdash") + geom_vline(xintercept = 200, linetype = "longdash") + geom_vline(xintercept = 330, linetype = "longdash") + labs(x = "",
         y = "H1.5 Coverage",
         color = "") +
    scale_color_manual(values = colors) + theme_bw() +  scale_x_continuous(breaks = NULL)

pdf("mean_plot_h15_intron_cov.pdf")
affected <- data.frame(H15_introns_data[,2])
unaffected <- data.frame(H15_introns_data[,1])
affected$Group <- as.factor('affected')
names(affected)[1] <- 'H1.5-Coverage'
unaffected$Group <- as.factor('unaffected')
names(unaffected)[1] <- 'H1.5-Coverage'
data_to_plot_affect <- rbind(affected,unaffected)
compare_means(`H1.5-Coverage` ~ Group, data =  data_to_plot_affect)
p <- ggboxplot(data_to_plot_affect, x = "Group", y = "H1.5-Coverage",
          color = rev(c("Unaffected" = "red1", "Affected" = "red4"))) +
  stat_compare_means(label = "p.signif",ref.group = "unaffected")
p + rremove("x.text") + rremove("x.title")




print(p)
dev.off()


```


## Intron_len and exon_len - exons H1.2-1.5

```{r}

affected <- read.table("intron_len_affected_h12_exons.tab",header= TRUE,fill = TRUE)
unaffected <- read.table("intron_len_unaffected_h12_exons.tab",header= TRUE,fill = TRUE)
affected <- data.frame(affected[which(affected < 12000 & 2000 < affected),])
unaffected <- data.frame(unaffected[which(unaffected < 12000 &  2000 < unaffected),])
affected$Group <- as.factor('affected')
names(affected)[1] <- 'length'
unaffected$Group <- as.factor('unaffected')
names(unaffected)[1] <- 'length'
data_to_plot_affect <- rbind(affected,unaffected)
compare_means(length ~ Group, data =  data_to_plot_affect, method = "t.test")
# pdf("h12_exons_intron_len.pdf")
p <- ggboxplot(data_to_plot_affect, x = "Group", y = "length",
          color = rev(c("Unaffected" = "deepskyblue", "Affected" = "navyblue"))) +
  stat_compare_means(label = "p.signif",ref.group = "unaffected")
p + rremove("x.text") + rremove("x.title")
# print(p)
# dev.off()
affected <- read.table("exon_len_affected_h12_exons.tab",header= TRUE,fill = TRUE)
unaffected <- read.table("exon_len_unaffected_h12_exons.tab",header= TRUE,fill = TRUE)
affected <- data.frame(affected[which(affected < 225),])
unaffected <- data.frame(unaffected[which(unaffected < 225),])
affected$Group <- as.factor('affected')
names(affected)[1] <- 'length'
unaffected$Group <- as.factor('unaffected')
names(unaffected)[1] <- 'length'
data_to_plot_affect <- rbind(affected,unaffected)
compare_means(length ~ Group, data =  data_to_plot_affect, method = "t.test")
pdf("h12_exons_exon_len.pdf")
p <- ggboxplot(data_to_plot_affect, x = "Group", y = "length",
          color = rev(c("Unaffected" = "deepskyblue", "Affected" = "navyblue"))) +
  stat_compare_means(label = "p.signif",ref.group = "unaffected")
p + rremove("x.text") + rremove("x.title")
print(p)
dev.off()
```


## Intron_len and exon_len - introns H1.2-H1.5



```{r}
affected <- read.table("len_affected_introns_int.tab",header= TRUE,fill = TRUE)
unaffected <- read.table("len_unaffected_introns_int.tab",header= TRUE,fill = TRUE)
affected <- data.frame(affected[which(affected < 9000 & 1000 < affected),])
unaffected <- data.frame(unaffected[which(unaffected < 9000 &  1000 < unaffected),])
affected$Group <- as.factor('affected')
names(affected)[1] <- 'length'
unaffected$Group <- as.factor('unaffected')
names(unaffected)[1] <- 'length'
data_to_plot_affect <- rbind(affected,unaffected)
compare_means(length ~ Group, data =  data_to_plot_affect, method = "t.test")
pdf("h12_introns_intron_len.pdf")
p <- ggboxplot(data_to_plot_affect, x = "Group", y = "length",
          color = rev(c("Unaffected" = "red1", "Affected" = "red4"))) +
  stat_compare_means(label = "p.signif",ref.group = "unaffected")
p + rremove("x.text") + rremove("x.title")
print(p)
dev.off()
affected <- read.table("exon_len_affected_h12_introns.tab",header= TRUE,fill = TRUE)
unaffected <- read.table("exon_len_unaffected_h12_introns.tab",header= TRUE,fill = TRUE)
affected <- data.frame(affected[which(affected < 225),])
unaffected <- data.frame(unaffected[which(unaffected < 225),])
affected$Group <- as.factor('affected')
names(affected)[1] <- 'length'
unaffected$Group <- as.factor('unaffected')
names(unaffected)[1] <- 'length'
data_to_plot_affect <- rbind(affected,unaffected)
compare_means(length ~ Group, data =  data_to_plot_affect, method = "t.test")
pdf("h12_introns_exon_len.pdf")
p <- ggboxplot(data_to_plot_affect, x = "Group", y = "length",
          color = rev(c("Unaffected" = "red1", "Affected" = "red4"))) +
  stat_compare_means(label = "p.signif",ref.group = "unaffected")
p + rremove("x.text") + rremove("x.title")
print(p)
dev.off()
```



